\documentclass[letterpaper,10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}

\setlist{noitemsep}
\pagestyle{empty}

\begin{document}

\begin{center}
\textbf{\large Srivathsan (Sri) Badrinarayanan}\\[2pt]
\href{mailto:srivathsanb14@gmail.com}{srivathsanb14@gmail.com} \, \textbullet \, +1 (412)-310-2420 \, \textbullet \,
\href{https://www.linkedin.com/in/srivathsan-badrinarayanan}{LinkedIn} \, \textbullet \,
\href{https://scholar.google.com/citations?user=0rwC4GQAAAAJ&hl=en&oi=ao}{Google Scholar} \, \textbullet \,
\href{https://orcid.org/0009-0004-6517-3145}{ORCID}
\end{center}

\vspace{0.4em}
\noindent
Developing physics-informed AI that unifies molecular language, graph, and 3D representations for therapeutic and materials discovery in data-limited settings.

\section*{EDUCATION}
\noindent
\textbf{Carnegie Mellon University}, Pittsburgh, PA \hfill August 2026 -- Present\\
Ph.D. in Mechanical Engineering, MAIL Lab

\noindent
\textbf{Carnegie Mellon University}, Pittsburgh, PA \hfill August 2023 -- December 2024\\
M.S. Artificial Intelligence Engineering -- Chemical Engineering \hfill GPA: 4.0/4.0

\noindent
\textbf{Indian Institute of Technology Madras}, Chennai, India \hfill July 2019 -- July 2023\\
B.Tech Chemical Engineering (Minor: Bioprocess Engineering)

\section*{PUBLICATIONS}
\noindent\textbf{Peer-Reviewed Journal Articles}
\begin{itemize}
    \item J. Ock, \textbf{S. Badrinarayanan}, R. Magar, A. Antony, A.B. Farimani. Multimodal Language and Graph Learning of Adsorption Configuration in Catalysis. \textit{Nature Machine Intelligence}, 2024.
    \item \textbf{S. Badrinarayanan}, C. Guntuboina, P. Mollaei, A.B. Farimani. Multi-Peptide: Multimodality Leveraged Language-Graph Learning of Peptide Properties. \textit{ACS JCIM}, 2024.
    \item \textbf{S. Badrinarayanan}, R. Magar, A. Antony, R.S. Meda, A.B. Farimani. MOFGPT: Generative Design of Metal-Organic Frameworks using Language Models. \textit{ACS JCIM}, 2025.
    \item T. Zeng, \textbf{S. Badrinarayanan}, J. Ock, C.K. Lai, A.B. Farimani. LLM-guided Chemical Process Optimization with a Multi-Agent Approach. \textit{ML: Science \& Technology}, 2025.
    \item J. Ock, R.S. Meda, \textbf{S. Badrinarayanan}, N.S. Aluru, A. Chandrasekhar, A.B. Farimani. Large Language Model Agent for Modular Task Execution in Drug Discovery. \textit{ACS JCIM}, 2026.
\end{itemize}

\noindent\textbf{Preprints \& Under Review}
\begin{itemize}
    \item \textbf{S. Badrinarayanan}, Y. Su, J. Ock, A. Pham, S. Ahuja, A.B. Farimani. Meta-Learning for Cross-Task Generalization in Protein Mutation Property Prediction. \textit{arXiv}, 2025. Under review, ACS JCIM.
    \item O. Issakah, \textbf{S. Badrinarayanan}, R.F. Saraf, J. Ock. Graph-Based Kirchhoff Modeling of Non-Ohmic Electron Transport in Self-Assembled Nanonecklace Networks. \textit{arXiv}, 2026.
\end{itemize}

\section*{ACADEMIC RESEARCH EXPERIENCE}
\noindent\textbf{Carnegie Mellon University}, MAIL Lab \hfill May 2024 -- June 2025\\
Graduate Researcher \hfill Advisor: Dr. Amir Barati Farimani
\begin{itemize}
    \item Multimodal and generative AI for peptides, catalysts, MOFs, and agentic drug discovery; five peer-reviewed publications.
    \item Multi-Peptide (JCIM 2024), Multimodal Catalysis (Nature MI 2024), MOFGPT (JCIM 2025), Drug Discovery Agent (JCIM 2026).
    \item Meta-learning preprint for protein mutation prediction. Mentored junior researchers; founded DreamPods.
\end{itemize}

\noindent\textbf{University of Alberta} \hfill May 2022 -- August 2022\\
MITACS Globalink Research Intern \hfill Advisor: Dr. Zukui Li
\begin{itemize}
    \item LSTM and Neural CDE surrogates for refinery flow-rate optimization. \href{https://www.youtube.com/watch?v=bidVGSq0R5o}{3MT talk}.
\end{itemize}

\noindent\textbf{IIT Madras} \hfill June 2021 -- May 2022\\
Research Fellow (Young Research Fellowship)
\begin{itemize}
    \item ML surrogates for stiff chemical kinetics; reduced CFD simulation time by 90\%.
\end{itemize}

\section*{INDUSTRY EXPERIENCE}
\noindent\textbf{Aikium Inc.}, Berkeley, CA \hfill June 2025 -- August 2025\\
Machine Learning Engineer
\begin{itemize}
    \item Multi-agent protein engineering pipelines (ESM, ProteinMPNN, AlphaFold, RFdiffusion) and LangChain interface for wet-lab scientists.
\end{itemize}

\noindent\textbf{Stealth Startup}, San Francisco Bay Area \hfill November 2025 -- June 2026\\
Founding Engineer
\begin{itemize}
    \item End-to-end ML, systems, and deployment across multiple 0$\to$1 product pivots.
\end{itemize}

\section*{LEADERSHIP \& RECOGNITION}
\begin{itemize}
    \item Founder, Generative AI Initiatives at CMU (DreamPods podcast, GenAI education platform).
    \item Peer Reviewer, \textit{ACS JCIM} (2025--present).
    \item MITACS Globalink Scholar (2022); Young Research Fellowship, IIT Madras (2021).
    \item Best Poster Award, Generative AI Course, CMU (2024).
\end{itemize}

\section*{TECHNICAL SKILLS}
\noindent
PyTorch, Transformers, GNNs, Diffusion, LLMs, RAG, RL (PPO, RLHF), Multimodal Learning, AlphaFold, ESM, ProteinMPNN, RFdiffusion, RDKit, Python, C++, R, LangChain, HuggingFace, Docker, AWS, CUDA, PostgreSQL, W\&B

\end{document}
